### 2022-01-19 manuscript/manuscript.Rmd
adding SAH info

affiliation:
  - id: '1'
    institution: 'Department of Psychology, University of Amsterdam'
  - id: '2'
    institution: 'Meta-Research Innovation Center at Stanford (METRICS), Stanford University'
  - id: '3'
    institution: 'Department of the Study of Religion, Aarhus University'
  - id: '4'
    institution: 'Department of Psychology, Princeton University'
  - id: '5'
    institution: 'Charité – Universitätsmedizin Berlin'
  - id: '6'
    institution: 'Meta-Research Innovation Center at Stanford (METRICS)'
  - id: '7'
    institution: 'School of Psychology, Cardiff University'
  - id: '8'
    institution: 'School of Psychological Science, Univeristy of Bristol'
  - id: '9'
    institution: 'Meta-Research Innovation Center Berlin (METRIC-B), QUEST Center for Transforming Biomedical Research, Berlin Institute of Health, Charité – Universitätsmedizin Berlin AND Departments of Medicine, Epidemiology and Population Health, Biomedical Data Science, and Statistics, Stanford University'
  - id: '10'
    institution: 'Univeristy of Melbourne'

@@

# Author contributions
Conceptualization: T.E.H. and J.P.A.I. Data curation: T.E.H. Formal analysis: T.E.H. Investigation: T.E.H., R.T.T., T.B., J.E.K., L.T., and V.E.K. Methodology: T.E.H., R.T.T., T.B., and J.P.A.I. Project administration: T.E.H. Resources: T.E.H. Software: T.E.H. Supervision: T.E.H. and J.P.A.I. Validation: T.E.H. Visualization: T.E.H. Writing - original draft: T.E.H. Writing - review & editing: T.E.H., R.T.T., T.B., L.T., and J.P.A.I.

>>>>

affiliation:
  - id: '1'
    institution: 'Department of Psychology, University of Amsterdam'
  - id: '2'
    institution: 'Meta-Research Innovation Center at Stanford (METRICS), Stanford University'
  - id: '3'
    institution: 'Department of the Study of Religion, Aarhus University'
  - id: '4'
    institution: 'Department of Psychology, Princeton University'
  - id: '5'
    institution: 'Charité – Universitätsmedizin Berlin'
  - id: '6'
    institution: 'Meta-Research Innovation Center at Stanford (METRICS)'
  - id: '7'
    institution: 'School of Psychology, Cardiff University'
  - id: '8'
    institution: 'School of Psychological Science, Univeristy of Bristol'
  - id: '9'
    institution: 'Meta-Research Innovation Center Berlin (METRIC-B), QUEST Center for Transforming Biomedical Research, Berlin Institute of Health, Charité – Universitätsmedizin Berlin AND Departments of Medicine, Epidemiology and Population Health, Biomedical Data Science, and Statistics, Stanford University'
  - id: '10'
    institution: 'Florey Department of Neuroscience and Mental Health, Univeristy of Melbourne'

@@

# Author contributions
Conceptualization: T.E.H. and J.P.A.I. Data curation: T.E.H. Formal analysis: T.E.H. Investigation: T.E.H., R.T.T., T.B., J.E.K., L.T., S.A.H., and V.E.K. Methodology: T.E.H., R.T.T., T.B., and J.P.A.I. Project administration: T.E.H. Resources: T.E.H. Software: T.E.H. Supervision: T.E.H. and J.P.A.I. Validation: T.E.H. Visualization: T.E.H. Writing - original draft: T.E.H. Writing - review & editing: T.E.H., R.T.T., T.B., L.T., and J.P.A.I.
